### 2010-04-29 docs/architecture/architecture.tex
add Ann's explaination of a layout

\subsection{\boxarray}

A \boxarray\ is an array of boxes

\subsection{\mlboxarray}

A \mlboxarray\ is a collection of \boxarray s at different levels of
refinement.

\subsection{\mllayout}

>>>>

\subsection{\boxarray\ and \mlboxarray}

A \boxarray\ is an array of boxes.  A \mlboxarray\ is a collection of
\boxarray s at different levels of refinement.

\subsection{\layout\ and \mllayout}

A \layout\ is basically a \boxarray\ that knows information about other
boxes, or box ``connectivity.''  It contains additional information
that is used in filling ghost cells from other fine grids or from
coarser grids.  This information is stored as long as the layout
exists so that we don't have to recompute intersections every time we
do some operation with two multifabs that have that layout, for
example.
